---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# HighlyReplicatedRNASeq

<!-- badges: start -->
<!-- badges: end -->

> Collection of Bulk RNA-Seq Experiments With Many Replicates

The HighlyReplicatedRNASeq package provides access to the count matrix results
from studies with many replicates. These datasets can be valuable for
benchmarking tools designed to handle RNA-seq data.

## Installation

You can install the latest version of `r BiocStyle::Biocpkg("HighlyReplicatedRNASeq")` with

``` r
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("HighlyReplicatedRNASeq")
```

To get the latest development version, install the package from [Github](https://github.com/const-ae/HighlyReplicatedRNASeq)

``` r
# install.packages("devtools")
devtools::install_github("const-ae/HighlyReplicatedRNASeq")
```

## Datasets

+ Schurch et al. (2016): 86 samples of S. *cerevisiae* in two conditions
   - `Schurch16()` / `Schurch16_metadata()`


At the moment, this package contains only one dataset, but more datasets can be added in the future.


## Example

Load the `Schurch16` dataset by calling the corresponding function. The first time you run this command, it will download the dataset and will subsequently cache it in a directory that is by `getExperimentHubOption("CACHE")`.

```{r}
schurch_se <- HighlyReplicatedRNASeq::Schurch16()
schurch_se
```


## References

Schurch, N. J., Schofield, P., Gierliński, M., Cole, C., Sherstnev, A., Singh, V., … Barton, G. J. (2016). 
How many biological replicates are needed in an RNA-seq experiment and which differential expression tool should you use? \emph{RNA}, 22(6), 839–851. https://doi.org/10.1261/rna.053959.115
